\vspace{-1em}Guidance, please! Towards a framework for RDF-based constraint languages.

### 2015-07-16 paper/paper 2/dc-2015.tex
3.2

The properties describing a simple constrained are very structural. The central property is the \emph{constraining element} which refers to one of 103 contraining elements described in our technical report \cite{BoschNolleAcarEckert2015}. Constraining elements are for example taken from Description Logics, another concrete example would be 'regex' where a regular expression is checked against some property value. Sometimes the constraining elements directly correspond to a constraint type, sometime (as for regex) they are shared by several constraint types. Complex constraints again need several constraing elements to be expressed.

@@

The \emph{constraining element} is an intuitive term which indicates the actual type of constraint. For the majority of the constraint types, there is exactly one constraining element. For the constraint type \emph{property domain (R-25, R-26)} whose constraints restrict domains of properties, e.g., there is only one constraining element with exactly the same identifier \emph{property domain}. For a few constraint types, however, one constraining element is not sufficient to describe all possible constraints of a particular constraint type and therefore multiple constraining elements may be stated. The constraint type \emph{language tag cardinality (R-48, R-49)}, for instance, is used to restrict data properties to have a minimum, maximum, or exact number of relationships to literals with selected language tags. Thus, three constraining elements are needed to express each possible constraint of that constraint type.

>>>>

The properties describing a simple constrained are very structural. The central property is the \emph{constraining element} which refers to one of 103 contraining elements described in our technical report \cite{BoschNolleAcarEckert2015}. Constraining elements are for example taken from Description Logics, another concrete example would be 'regex' where a regular expression is checked against some property value. In most cases, constraining elements directly correspond to a constraint type, sometimes (as for regex) they are shared by several constraint types. Complex constraints again need several constraing elements to be expressed.

@@

The \emph{constraining element} is an intuitive term which indicates the actual type of constraint. For the majority of the constraint types, there is exactly one constraining element. Complex constraints need several constraining elements to be expressed. For the constraint type \emph{property domain (R-25, R-26)} whose constraints restrict domains of properties, e.g., there is only one constraining element with exactly the same identifier \emph{property domain}. For some constraint types, however, one constraining element is not sufficient to describe all possible constraints of a particular constraint type and therefore multiple constraining elements may be stated. The constraint type \emph{language tag cardinality (R-48, R-49)}, for instance, is used to restrict data properties to have a minimum, maximum, or exact number of relationships to literals with selected language tags. Thus, three constraining elements are needed to express each possible constraint of that constraint type.
